Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2024-05-28 paper/fig/arh_binomial_mones.tex
mones

\begin{tikzpicture}
    \pgfplotsset{
        scale only axis,
        % height=4cm,
        xlabel={total daily new hospitalizations},
        ylabel={total lost contacts},
        width=0.45\textwidth,
        every axis title/.append style={at={(0.45,0.0)}},
        x dir= reverse,
        y dir= reverse,
    }
    \begin{groupplot}[
        group style={
            group size=2 by 3,
            y descriptions at=edge left,
            x descriptions at=edge bottom,
            vertical sep=0pt,
            horizontal sep=0pt,
        },
        % legend entries={{$\text{PCN}_{b=2}$}, {$\text{PCN}_{b=3}$}, {$\text{PCN}_{b=4}$}, {$\text{PCN}_{b=5}$}, {$\text{PCN}$}, {Fixed}},
    ]
    % interpolated plot for ARI
    \nextgroupplot[mark size=1pt,draw opacity=1,legend entries={{$\text{PCN}_{b=2}$}, {$\text{PCN}_{b=3}$}, {$\text{PCN}_{b=4}$}, {$\text{PCN}_{b=5}$}, {$\text{PCN}$}, {Fixed}},title={$\mdprewardfn_\text{ARI}$, different budgets}]
    % mean line
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[fill opacity=0.5,\c] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/cs/ari/binomial/interpolated/budget_\b.csv};
        }
        \temp
    }
    % std fillbetween, has to be after means for legend order
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[name path=upper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/ari/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=lower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/ari/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[\c!15] fill between[of={upper\b} and {lower\b}];
        }
        \temp
    }
    \addplot[only marks,mark=+] table [x expr=-1*\thisrow{o_0}, y expr=-1*\thisrow{o_1}, col sep=comma] {data/cs/cs_fixed.csv};
    % ARI vs ARH per budget
    \pgfplotsforeachungrouped \b in {2, 3, 4, 5, {None}}
    {
        % mean plots
        \edef\temp{
            \noexpand\nextgroupplot[draw opacity=1,legend entries={$R_{\text{ARH}}$, $R_{\text{ARI}}$},title={$\text{PCN}_{b=\b}$}]
            \noexpand\addplot[fill opacity=0.5,pc1] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[fill opacity=0.5,pc2] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/cs/ari/binomial/interpolated/budget_\b.csv};
            % std plots
            \noexpand\addplot[name path=binomialupper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=binomiallower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[pc1!15] fill between[of={binomialupper\b} and {binomiallower\b}];

            \noexpand\addplot[name path=odeupper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/ari/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=odelower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/ari/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[pc2!15] fill between[of={odeupper\b} and {odelower\b}];
        }
        \temp
    }
    \end{groupplot}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
    \pgfplotsset{
        scale only axis,
        % height=4cm,
        xlabel={total daily new hospitalizations},
        ylabel={total lost contacts},
        width=0.45\textwidth,
        every axis title/.append style={at={(0.45,0.0)}},
        x dir= reverse,
        y dir= reverse,
    }
    \begin{groupplot}[
        group style={
            group size=2 by 3,
            y descriptions at=edge left,
            x descriptions at=edge bottom,
            vertical sep=0pt,
            horizontal sep=0pt,
        },
        % legend entries={{$\text{PCN}_{b=2}$}, {$\text{PCN}_{b=3}$}, {$\text{PCN}_{b=4}$}, {$\text{PCN}_{b=5}$}, {$\text{PCN}$}, {Fixed}},
    ]
    % interpolated plot for MONES
    \nextgroupplot[mark size=1pt,draw opacity=1,legend entries={{$\text{MONES}_{b=2}$}, {$\text{MONES}_{b=3}$}, {$\text{MONES}_{b=4}$}, {$\text{MONES}_{b=5}$}, {$\text{MONES}$}, {Fixed}},title={MONES algorithm, different budgets}]
    % mean line
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[fill opacity=0.5,\c] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
        }
        \temp
    }
    % std fillbetween, has to be after means for legend order
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[name path=upper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=lower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[\c!15] fill between[of={upper\b} and {lower\b}];
        }
        \temp
    }
    \addplot[only marks,mark=+] table [x expr=-1*\thisrow{o_0}, y expr=-1*\thisrow{o_1}, col sep=comma] {data/cs/cs_fixed.csv};
    % ARI vs ARH per budget
    \pgfplotsforeachungrouped \b in {2, 3, 4, 5, {None}}
    {
        % mean plots
        \edef\temp{
            \noexpand\nextgroupplot[draw opacity=1,legend entries={$\text{PCN}_{b=\b}$, $\text{MONES}_{b=\b}$},title={budget \b}]
            \noexpand\addplot[fill opacity=0.5,pc1] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[fill opacity=0.5,pc2] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            % std plots
            \noexpand\addplot[name path=binomialupper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=binomiallower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[pc1!15] fill between[of={binomialupper\b} and {binomiallower\b}];

            \noexpand\addplot[name path=odeupper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=odelower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[pc2!15] fill between[of={odeupper\b} and {odelower\b}];
        }
        \temp
    }
    \end{groupplot}
\end{tikzpicture}

### 2024-05-28 paper/fig/arh_ode_mones.tex
mones

\begin{tikzpicture}
    \pgfplotsset{
        scale only axis,
        % height=4cm,
        xlabel={total daily new hospitalizations},
        ylabel={total lost contacts},
        width=0.45\textwidth,
        every axis title/.append style={at={(0.45,0.0)}},
        x dir= reverse,
        y dir= reverse,
    }
    \begin{groupplot}[
        group style={
            group size=2 by 3,
            y descriptions at=edge left,
            x descriptions at=edge bottom,
            vertical sep=0pt,
            horizontal sep=0pt,
        },
        % legend entries={{$\text{PCN}_{b=2}$}, {$\text{PCN}_{b=3}$}, {$\text{PCN}_{b=4}$}, {$\text{PCN}_{b=5}$}, {$\text{PCN}$}, {Fixed}},
    ]
    % interpolated plot for MONES
    \nextgroupplot[mark size=1pt,draw opacity=1,legend entries={{$\text{MONES}_{b=2}$}, {$\text{MONES}_{b=3}$}, {$\text{MONES}_{b=4}$}, {$\text{MONES}_{b=5}$}, {$\text{MONES}$}, {Fixed}},title={MONES algorithm, different budgets}]
    % mean line
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[fill opacity=0.5,\c] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
        }
        \temp
    }
    % std fillbetween, has to be after means for legend order
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[name path=upper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=lower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[\c!15] fill between[of={upper\b} and {lower\b}];
        }
        \temp
    }
    \addplot[only marks,mark=+] table [x expr=-1*\thisrow{o_0}, y expr=-1*\thisrow{o_1}, col sep=comma] {data/cs/cs_fixed.csv};
    % ARI vs ARH per budget
    \pgfplotsforeachungrouped \b in {2, 3, 4, 5, {None}}
    {
        % mean plots
        \edef\temp{
            \noexpand\nextgroupplot[draw opacity=1,legend entries={$\text{PCN}_{b=\b}$, $\text{MONES}_{b=\b}$},title={budget \b}]
            \noexpand\addplot[fill opacity=0.5,pc1] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[fill opacity=0.5,pc2] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            % std plots
            \noexpand\addplot[name path=binomialupper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=binomiallower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[pc1!15] fill between[of={binomialupper\b} and {binomiallower\b}];

            \noexpand\addplot[name path=odeupper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=odelower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[pc2!15] fill between[of={odeupper\b} and {odelower\b}];
        }
        \temp
    }
    \end{groupplot}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
    \pgfplotsset{
        scale only axis,
        % height=4cm,
        xlabel={total daily new hospitalizations},
        ylabel={total lost contacts},
        width=0.45\textwidth,
        every axis title/.append style={at={(0.45,0.0)}},
        x dir= reverse,
        y dir= reverse,
    }
    \begin{groupplot}[
        group style={
            group size=2 by 3,
            y descriptions at=edge left,
            x descriptions at=edge bottom,
            vertical sep=0pt,
            horizontal sep=0pt,
        },
        % legend entries={{$\text{PCN}_{b=2}$}, {$\text{PCN}_{b=3}$}, {$\text{PCN}_{b=4}$}, {$\text{PCN}_{b=5}$}, {$\text{PCN}$}, {Fixed}},
    ]
    % interpolated plot for MONES
    \nextgroupplot[mark size=1pt,draw opacity=1,legend entries={{$\text{MONES}_{b=2}$}, {$\text{MONES}_{b=3}$}, {$\text{MONES}_{b=4}$}, {$\text{MONES}_{b=5}$}, {$\text{MONES}$}, {Fixed}},title={MONES algorithm, different budgets}]
    % mean line
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[fill opacity=0.5,\c] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/mones/arh/ode/interpolated/budget_\b.csv};
        }
        \temp
    }
    % std fillbetween, has to be after means for legend order
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[name path=upper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/ode/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=lower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/ode/interpolated/budget_\b.csv};
            \noexpand\addplot[\c!15] fill between[of={upper\b} and {lower\b}];
        }
        \temp
    }
    \addplot[only marks,mark=+] table [x expr=-1*\thisrow{o_0}, y expr=-1*\thisrow{o_1}, col sep=comma] {data/cs/cs_fixed.csv};
    % ARI vs ARH per budget
    \pgfplotsforeachungrouped \b in {2, 3, 4, 5, {None}}
    {
        % mean plots
        \edef\temp{
            \noexpand\nextgroupplot[draw opacity=1,legend entries={$\text{PCN}_{b=\b}$, $\text{MONES}_{b=\b}$},title={budget $\b$}]
            \noexpand\addplot[fill opacity=0.5,pc1] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/cs/arh/ode/interpolated/budget_\b.csv};
            \noexpand\addplot[fill opacity=0.5,pc2] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}, col sep=comma] {data/mones/arh/ode/interpolated/budget_\b.csv};
            % std plots
            \noexpand\addplot[name path=binomialupper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/ode/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=binomiallower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/ode/interpolated/budget_\b.csv};
            \noexpand\addplot[pc1!15] fill between[of={binomialupper\b} and {binomiallower\b}];

            \noexpand\addplot[name path=odeupper\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/ode/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=odelower\b, draw=none] table [x expr=-1*\noexpand\thisrow{mu_o_1}, y expr=-1*\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/mones/arh/ode/interpolated/budget_\b.csv};
            \noexpand\addplot[pc2!15] fill between[of={odeupper\b} and {odelower\b}];
        }
        \temp
    }
    \end{groupplot}
\end{tikzpicture}
